Fully structured proof theory for intuitionistic modal logics

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
fixing some other figures

% definitions specific to your article
%\newcommand{\ob}{[}
%\newcommand{\cb}{]}

%\input{macros}
\definecolor{notgreen}{rgb}{.1,.6,.1}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\blue}[1]{{\color{blue}{#1}}}
\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}

%%% General

\newcommand{\F}{\mathcal{F}}
\newcommand{\M}{\mathcal{M}}
%\newcommand{\G}{\mathcal{G}}

\newcommand{\B}{\mathcal{B}}
\newcommand{\Left}{\mathcal{L}}
\newcommand{\Right}{\mathcal{R}}

\newcommand*{\rel}{R}
\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
\newcommand*{\invr}[1]{#1^\mathsf{inv}}

\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}

\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Logic
\newcommand*{\ax}[1]{\mathsf{#1}}
\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
\newcommand*{\A}{\mathcal{A}}

\newcommand{\force}[2]{#1\Vdash#2}
\newcommand{\nforce}[2]{#1\nVdash#2}
%
\newcommand{\height}[1]{|#1|}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Systems
\newcommand*{\K}{\mathsf{K}}
\newcommand*{\IK}{\mathsf{IK}}
\newcommand*{\lab}{\mathsf{lab}}
\newcommand*{\n}{\mathsf{n}}

%%% Connectives
\newcommand*{\NOT}{\neg}
\newcommand*{\AND}{\mathbin{\wedge}}
\newcommand*{\TOP}{\mathord{\top}}
\newcommand*{\OR}{\mathbin{\vee}}
\newcommand*{\BOT}{\mathord{\bot}}
\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}

\newcommand*{\BOX}{\mathord{\Box}}
\newcommand*{\DIA}{\mathord{\Diamond}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Nested sequents
\newcommand*\mdelim[3]{%
	\mathopen{}\left#1%
	#3%
	\right#2\mathclose{}%
}

\makeatletter
%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
\newcommand*{\BR}{%
\@ifnextchar\i{\br@two}{%
\@ifnextchar\bgroup{\br@one}{% 
}}}
\newcommand*{\br@one}[1]{%
\def\br@{#1}%
\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
}
\newcommand*{\br@two}[3]{%
\def\br@{#3}%
\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
}
%
\newcommand*{\bBR}{%
\@ifnextchar\i{\bbr@two}{%
\@ifnextchar\bgroup{\bbr@one}{% 
}}}
\newcommand*{\bbr@one}[1]{%
\def\br@{#1}%
\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
}
\newcommand*{\bbr@two}[3]{%
\def\br@{#3}%
\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
}
%
%\newcommand*{\@makeoperator}[2]{
%	\newcommand*{#1}{%
%		\mathrm{#2}\mdelim{\lparen}{\rparen}
%	}
%}
%%
%\@makeoperator{\fm}{fm^{\n}}
%\@makeoperator{\ofm}{fm^{\o}}
%\@makeoperator{\hfm}{fm^{\h}}
%%
%\@makeoperator{\depth}{dp}
%\@makeoperator{\rank}{rk}
%\@makeoperator{\height}{ht}
%\@makeoperator{\tree}{tree}
%\@makeoperator{\graph}{graph}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% contexts
\makeatletter
\newcommand*{\cxs}{%
\@ifnextchar\i{\cxs@two}{%
\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
}}}
\newcommand*{\cxs@one}[1]{%
\def\cxs@{#1}%
\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
\cxs@one@decor%
}
\newcommand*{\cxs@two}[3]{%
\def\cxs@{#3}%
\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
\cxs@one@decor%
}
\def\cxs@one@decor{%
\@ifnextchar_{\cxs@one@sub}{%
\@ifnextchar^{\cxs@one@sup}{%
	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
		\@ifnextchar[{\cxs@one@arg}%]
		\cxs}}}%
}
\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}

%% Change these as needed, but keep the \cx@continuation at the end
\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}

\def\cx@delete@star#1*{%
\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
}

\newcommand*{\@makecontextual}[2]{
\newcommand*{#1}{%
\@ifnextchar*{\cx@delete@star{#2}}{%
	\@ifnextchar\f{\cx@delete@focus{#2}}{%
		#2\cx@continuation}}%
}%
}
\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}

\@makecontextual{\Ex}{}

\@makecontextual{\Cx}{\Gamma}
\@makecontextual{\Dx}{\Delta}
\@makecontextual{\Lx}{\Lambda}
\@makecontextual{\Rx}{\Pi}

\@makecontextual{\LLx}{\Omega}
\@makecontextual{\RRx}{\Xi}
\@makecontextual{\CCx}{\Sigma}
\@makecontextual{\DDx}{\Theta}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% intuitionistic
\newcommand*{\rt}[1]{#1^\circ}
\newcommand*{\lf}[1]{#1^\bullet}

%%% Extracting symbols from MnSymbol 
\DeclareFontFamily{U} {MnSymbolC}{}
%
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
<-6>  MnSymbolC5
<6-7>  MnSymbolC6
<7-8>  MnSymbolC7
<8-9>  MnSymbolC8
<9-10> MnSymbolC9
<10-12> MnSymbolC10
<12->   MnSymbolC12}{}
\DeclareFontShape{U}{MnSymbolC}{b}{n}{
<-6>  MnSymbolC-Bold5
<6-7>  MnSymbolC-Bold6
<7-8>  MnSymbolC-Bold7
<8-9>  MnSymbolC-Bold8
<9-10> MnSymbolC-Bold9
<10-12> MnSymbolC-Bold10
<12->   MnSymbolC-Bold12}{}
%
\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
%
\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}

%%% Labelled sequents
\newcommand{\SEQ}{\Rightarrow}
\newcommand*{\DD}{\mathcal{D}}
%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%\newcommand*{\invr}[1]{#1^\bullet}
%\newcommand*{\rel}{R}

%%% Labelled rules
\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%
\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
%
\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}

\newcommand*{\labIKp}{\lab\IK_{\le}}
\newcommand*{\nIKp}{\n\IK_{\le}}

@@

\begin{figure}%[h]
	\centering
	\small
	\fbox{
		\begin{minipage}{.95\textwidth}
			\begin{tabular}{@{\!}c@{\quad}c}
				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A} }{}$
				&
				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
%				\quad
%				$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
				\\\\
				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
				&
				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
				\\\\
				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\llabrn\IMP}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, \futs xy, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
				}
				\\\\
				\multicolumn{2}{c}{
					$\vliinf{\rlabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$ 
					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
				}
				\\\\
				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $\lb y, \lb z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
				\\\\
				$\vlinf{\llabrn\DIA}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
				\\
				\multicolumn{2}{c}{
					$\mbox{\hbox to .9\linewidth{\dotfill}}$
				}
				\\
				$\vlinf{\rn{refl_\le}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
				&
				$\vlinf{\rn{trans_\le}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\rn{F_1}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
				}
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\rn{F_2}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy,\futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
				}
			\end{tabular}		
		\end{minipage}
	}		
	\caption{System $\labIKp$}
	\label{fig:labIKp}
\end{figure}

@@

\begin{theorem}\label{thm:cutfree-compl}
	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
	%
	For any formula $A$, the following are equivalent.
	%
	\begin{enumerate}
		\item\label{i} $A$ is a theorem of $\IK$ 
		%
		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
		%		
		\smash{%\fbox{
			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
		}%}
		%
		\item\label{iii} $A$ is provable in $\labIKp$
		%
%		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
	\end{enumerate}
\end{theorem}

The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal} for details).
%%
%In particular, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
%%
%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
%
%\vspace*{-.9cm}
%$$
%\hspace*{-.5cm}
%\scalebox{.9}{
%	$
%	\vlderivation{
%		\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
%			\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
%				\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
%					\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
%						\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
%							\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
%								\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
%									\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
%										\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
%											\vlhy {}
%										}
%									}
%								}
%							}{
%								%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
%								%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
%								%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
%								%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
%								\vlhy {\qquad\vdots\qquad}
%								%										}
%								%									}
%								%								}
%								%							}
%							}
%						}
%					}
%				}
%			}
%		}
%	}$
%}$$
%%\end{example}
%
%%\vspace*{-.5cm}
%
%Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
%%
%We therefore have to show that such a rule is admissible in our system.
%%
%As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
%
%\vspace*{-.5cm}
%%\begin{example}
%$$
%\scalebox{.9}{
%	$
%	\vlderivation{
%		\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
%			\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
%				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
%					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
%						\vlhy{}
%					}
%				}
%			}
%		}
%	}
%	$
%}
%$$
%%\end{example}

>>>>

\input{macros}

%\definecolor{notgreen}{rgb}{.1,.6,.1}
%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
%\newcommand{\red}[1]{{\color{red}{#1}}}
%\newcommand{\blue}[1]{{\color{blue}{#1}}}
%\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
%\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
%
%%%% General
%
%\newcommand{\F}{\mathcal{F}}
%\newcommand{\M}{\mathcal{M}}
%%\newcommand{\G}{\mathcal{G}}
%
%\newcommand{\B}{\mathcal{B}}
%\newcommand{\Left}{\mathcal{L}}
%\newcommand{\Right}{\mathcal{R}}
%
%\newcommand*{\rel}{R}
%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
%
%\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
%\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
%\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%
%\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
%\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
%\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
%\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
%\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Logic
%\newcommand*{\ax}[1]{\mathsf{#1}}
%\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
%\newcommand*{\A}{\mathcal{A}}
%
%\newcommand{\force}[2]{#1\Vdash#2}
%\newcommand{\nforce}[2]{#1\nVdash#2}
%%
%\newcommand{\height}[1]{|#1|}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Systems
%\newcommand*{\K}{\mathsf{K}}
%\newcommand*{\IK}{\mathsf{IK}}
%\newcommand*{\lab}{\mathsf{lab}}
%\newcommand*{\n}{\mathsf{n}}
%
%%%% Connectives
%\newcommand*{\NOT}{\neg}
%\newcommand*{\AND}{\mathbin{\wedge}}
%\newcommand*{\TOP}{\mathord{\top}}
%\newcommand*{\OR}{\mathbin{\vee}}
%\newcommand*{\BOT}{\mathord{\bot}}
%\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
%
%\newcommand*{\BOX}{\mathord{\Box}}
%\newcommand*{\DIA}{\mathord{\Diamond}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Nested sequents
%\newcommand*\mdelim[3]{%
%	\mathopen{}\left#1%
%	#3%
%	\right#2\mathclose{}%
%}
%
%\makeatletter
%%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
%\newcommand*{\BR}{%
%\@ifnextchar\i{\br@two}{%
%\@ifnextchar\bgroup{\br@one}{% 
%}}}
%\newcommand*{\br@one}[1]{%
%\def\br@{#1}%
%\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
%}
%\newcommand*{\br@two}[3]{%
%\def\br@{#3}%
%\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
%}
%%
%\newcommand*{\bBR}{%
%\@ifnextchar\i{\bbr@two}{%
%\@ifnextchar\bgroup{\bbr@one}{% 
%}}}
%\newcommand*{\bbr@one}[1]{%
%\def\br@{#1}%
%\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
%}
%\newcommand*{\bbr@two}[3]{%
%\def\br@{#3}%
%\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
%}
%%
%%\newcommand*{\@makeoperator}[2]{
%%	\newcommand*{#1}{%
%%		\mathrm{#2}\mdelim{\lparen}{\rparen}
%%	}
%%}
%%%
%%\@makeoperator{\fm}{fm^{\n}}
%%\@makeoperator{\ofm}{fm^{\o}}
%%\@makeoperator{\hfm}{fm^{\h}}
%%%
%%\@makeoperator{\depth}{dp}
%%\@makeoperator{\rank}{rk}
%%\@makeoperator{\height}{ht}
%%\@makeoperator{\tree}{tree}
%%\@makeoperator{\graph}{graph}
%\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% contexts
%\makeatletter
%\newcommand*{\cxs}{%
%\@ifnextchar\i{\cxs@two}{%
%\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
%}}}
%\newcommand*{\cxs@one}[1]{%
%\def\cxs@{#1}%
%\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
%\cxs@one@decor%
%}
%\newcommand*{\cxs@two}[3]{%
%\def\cxs@{#3}%
%\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
%\cxs@one@decor%
%}
%\def\cxs@one@decor{%
%\@ifnextchar_{\cxs@one@sub}{%
%\@ifnextchar^{\cxs@one@sup}{%
%	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
%		\@ifnextchar[{\cxs@one@arg}%]
%		\cxs}}}%
%}
%\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
%\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
%\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
%
%%% Change these as needed, but keep the \cx@continuation at the end
%\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
%\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
%\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
%
%\def\cx@delete@star#1*{%
%\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
%}
%
%\newcommand*{\@makecontextual}[2]{
%\newcommand*{#1}{%
%\@ifnextchar*{\cx@delete@star{#2}}{%
%	\@ifnextchar\f{\cx@delete@focus{#2}}{%
%		#2\cx@continuation}}%
%}%
%}
%\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
%
%\@makecontextual{\Ex}{}
%
%\@makecontextual{\Cx}{\Gamma}
%\@makecontextual{\Dx}{\Delta}
%\@makecontextual{\Lx}{\Lambda}
%\@makecontextual{\Rx}{\Pi}
%
%\@makecontextual{\LLx}{\Omega}
%\@makecontextual{\RRx}{\Xi}
%\@makecontextual{\CCx}{\Sigma}
%\@makecontextual{\DDx}{\Theta}
%\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% intuitionistic
%\newcommand*{\rt}[1]{#1^\circ}
%\newcommand*{\lf}[1]{#1^\bullet}
%
%
%%%% Extracting symbols from MnSymbol 
%\DeclareFontFamily{U} {MnSymbolC}{}
%%
%\DeclareFontShape{U}{MnSymbolC}{m}{n}{
%<-6>  MnSymbolC5
%<6-7>  MnSymbolC6
%<7-8>  MnSymbolC7
%<8-9>  MnSymbolC8
%<9-10> MnSymbolC9
%<10-12> MnSymbolC10
%<12->   MnSymbolC12}{}
%\DeclareFontShape{U}{MnSymbolC}{b}{n}{
%<-6>  MnSymbolC-Bold5
%<6-7>  MnSymbolC-Bold6
%<7-8>  MnSymbolC-Bold7
%<8-9>  MnSymbolC-Bold8
%<9-10> MnSymbolC-Bold9
%<10-12> MnSymbolC-Bold10
%<12->   MnSymbolC-Bold12}{}
%%
%\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
%%
%\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
%\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
%
%
%%%% Labelled sequents
%\newcommand{\SEQ}{\Rightarrow}
%\newcommand*{\DD}{\mathcal{D}}
%%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
%%\newcommand*{\invr}[1]{#1^\bullet}
%%\newcommand*{\rel}{R}
%
%%%% Labelled rules
%\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
%\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
%\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%%
%\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
%\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
%%
%\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
%\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
%
%\newcommand*{\labIKp}{\lab\IK_{\le}}
%\newcommand*{\nIKp}{\n\IK_{\le}}

@@

\begin{figure}
	\centering
	\fbox{
		\includegraphics[scale=.8]{fig-labIK}
	}		
	\caption{System $\labIKp$}
	\label{fig:labIK}
\end{figure}

@@

\begin{theorem}\label{thm:cutfree-compl}
	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
	%
	For any formula $A$, the following are equivalent.
	%
	\begin{enumerate}
		\item\label{i} $A$ is a theorem of $\IK$ 
		%
		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with \quad
		%		
		\smash{\parbox[c]{5cm}{\includegraphics[scale=0.8]{cut}}}
		%
		\item\label{iii} $A$ is provable in $\labIKp$
		%
		%\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
	\end{enumerate}
\end{theorem}

The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal} for details).
